### 2014-12-13 Documentacion/reconstruccion.tex
se agrega una tabla, se empieza a trabajar en la máquina grande

PONER TABLA

>>>>

\begin{table}[h]
\begin{tabular}{ll|l|l|l|l|}
\cline{3-6}
                                                                              &                                                       & \multicolumn{2}{l|}{Algoritmo Viejo}                                                                                             & \multicolumn{2}{l|}{Algoritmo Nuevo}                                                                                            \\ \hline
\multicolumn{1}{|l|}{\begin{tabular}[c]{@{}l@{}}Marker\\ Ground\end{tabular}} & \begin{tabular}[c]{@{}l@{}}Name\\ Ground\end{tabular} & \begin{tabular}[c]{@{}l@{}}Error \\ Promedio\\ (cm)\end{tabular} & \begin{tabular}[c]{@{}l@{}}Percentil\\ 99\% (cm)\end{tabular} & \begin{tabular}[c]{@{}l@{}}Error\\ Promedio\\ (cm)\end{tabular} & \begin{tabular}[c]{@{}l@{}}Percentil\\ 99\% (cm)\end{tabular} \\ \hline
\multicolumn{1}{|l|}{1}                                                       & LeftUpLeg                                             & 0.4182                                                           & 3.7197                                                        & 0.3671                                                          & 0.5158                                                        \\ \hline
\multicolumn{1}{|l|}{2}                                                       & LeftLeg                                               & 0.3586                                                           & 0.5449                                                        & 0.3670                                                          & 0.5411                                                        \\ \hline
\multicolumn{1}{|l|}{3}                                                       & LeftFoot                                              & 0.3862                                                           & 1.0379                                                        & 0.3720                                                          & 0.5580                                                        \\ \hline
\multicolumn{1}{|l|}{4}                                                       & RightUpLeg                                            & 0.3963                                                           & 1.7542                                                        & 0.3714                                                          & 0.5879                                                        \\ \hline
\multicolumn{1}{|l|}{5}                                                       & RightLeg                                              & 0.3830                                                           & 0.9840                                                        & 0.3780                                                          & 0.5860                                                        \\ \hline
\multicolumn{1}{|l|}{6}                                                       & RightFoot                                             & 0.4192                                                           & 1.5364                                                        & 0.4212                                                          & 1.8483                                                        \\ \hline
\multicolumn{1}{|l|}{7}                                                       & Spine                                                 & 0.4075                                                           & 0.9092                                                        & 0.4040                                                          & 0.6043                                                        \\ \hline
\multicolumn{1}{|l|}{8}                                                       & Head                                                  & 0.4130                                                           & 1.2853                                                        & 0.3867                                                          & 0.9063                                                        \\ \hline
\multicolumn{1}{|l|}{9}                                                       & LeftArm                                               & 0.3626                                                           & 0.6394                                                        & 0.3666                                                          & 0.7997                                                        \\ \hline
\multicolumn{1}{|l|}{10}                                                      & LeftForeArm                                           & 0.4774                                                           & 2.8511                                                        & 0.3873                                                          & 0.9056                                                        \\ \hline
\multicolumn{1}{|l|}{11}                                                      & LeftHand                                              & 0.4217                                                           & 2.0700                                                        & 0.4007                                                          & 1.1722                                                        \\ \hline
\multicolumn{1}{|l|}{12}                                                      & RightArm                                              & 0.4756                                                           & 2.4363                                                        & 0.4025                                                          & 1.4771                                                        \\ \hline
\multicolumn{1}{|l|}{13}                                                      & RightForeArm                                          & 0.4590                                                           & 3.1711                                                        & 0.3844                                                          & 0.7810                                                        \\ \hline
\multicolumn{1}{|l|}{14}                                                      & RightHand                                             & 0.4545                                                           & 2.4782                                                        & 0.3816                                                          & 0.7728                                                        \\ \hline
\multicolumn{1}{l|}{}                                                         & Secuencia                                             & 0.38556                                                          & 1.7907                                                        & 0.35686                                                         & 0.81266                                                       \\ \cline{2-6} 
\end{tabular}
\end{table}
